Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}

### 2016-04-20 paper/paper.tex
local changes

MERGE HERE

ALSO TOPIC TABLE

>>>>

To answer the first question above, we have to turn to human intuition.  While the original problem was too massive for a human to take on, the LDA algorithm has produced the prescribed number of topics with the most common words for each topic.  This looks like:

The algorithm of course makes no attempt to interpret the meaning of this, as it simply looks for the words that generally appear together and lumps them into the specified number of topics.  At this point, we literally have to look through each topic and attempt to identify it.  For example, topic 6 seems to be about Israel with key words like ``israel'', ``palestinian'', and ``netanyahu'', while topic 8 seems to have a lot of common words like ``think'', ``like'', and ``good''.

After this, we have our overall topic table.

TOPIC TABLE HERE
